Online Verification of Commutativity

### 2020-08-11 acmPaper/paper.tex
Move RW to the end
Notation pass

We start by formalizing the notion of a diagram, drawing terminology from the previous acyclic work by Murota ~\cite{commutative}.

We start with a directed graph $G=(V,E)$, where $V$ consists of sets of elements and edges $(u, v)$ in $E$ correspond to functions that maps elements of $u$ to elements in $v$.
All these functions form a semigroup $F$, where multiplication is function composition.
A semigroup consists of a set and an associative binary operation, which we use to capture function composition.

The correspondence between edges and functions is stored as a mapping $f:E\rightarrow F$, where $f$ maps each edge to the function it represents.

A path is a sequence of edges. The edge-to-function mapping $f$ can be naturally extended to paths: if path $p=e_1\circ e_2 ... e_n$ then $f(p)=f(e_1) \circ f(e_2) ... f(e_n)$.

The notation $\partial(p)$ maps to the tuple (start node of $p$, end node of $p$).
Additionally, $\partial(p)^{+}$ is the start node, and $\partial(p)^{-}$ is end node of p.

A pair of paths $p$ and $q$ is called \textit{parallel} iff their terminal nodes are the same, i.e., $\partial(p)=\partial(q)$.
$\partial$, $\partial^{+}$ and $\partial^{-}$ are extended to apply to parallel pairs. For parallel pair $p$ = ($p_1$, $p_2$), $\partial(p)=\partial(p_1)=\partial(p_2)=(\partial(p)^{+}, \partial(p)^{-})$.
Let $R_{all}$ be the set of all parallel pairs of paths in the diagram.

The diagram commutes iff $f(p)=f(q)$ $\forall (p,q)\in R_{all}$; that is, the composition of maps along any path connecting $u$ to $v$ is independent of path choice.

>>>>

We start by formalizing the notion of a diagram, drawing terminology from the previous acyclic work by Murota~\cite{commutative}.

\paragraph{Notation.}

We start with a directed graph $G=(V,E)$, where $V$ corresponds to sets of elements and edges $(u, v)$ in $E$ correspond to functions that maps elements of $u$ to elements in $v$.
All these functions form a semigroup $F$, where multiplication is function composition.
A semigroup consists of a set and an associative binary operation, which we use to capture function composition.
%
The correspondence between edges and functions is stored as a mapping $f:E\rightarrow F$, where $f$ maps each edge to the function it represents.

A path is a sequence of edges. The edge-to-function mapping $f$ can be naturally extended to paths: if path $p=e_1\circ e_2 \circ \cdots \circ e_n$ then $f(p)=f(e_1) \circ f(e_2) \circ \cdots \circ f(e_n)$.
%
We write $\partial(p)^{+}$ for $p$'s start node, $\partial(p)^{-}$ for its end node, and $\partial(p)$ to denote the pair
$(\partial(p)^{+}, \partial(p)^{-})$.
\xxx[as]{Simplified this explanation; I hope it's OK.}

A pair of paths $p$ and $q$ is called \textit{parallel} iff their terminal nodes are the same, i.e., $\partial(p)=\partial(q)$.
$\partial$, $\partial^{+}$ and $\partial^{-}$ are extended to apply to parallel pairs.
\xxx[as]{Let's use a name other than $p$, which we have already used for paths, for pairs. (Or use something else for paths above.) Also, since we just used $p$ and $q$ for two paths, maybe that would be better than $p_1$ and $p_2$.}
For parallel pair $p$ = ($p_1$, $p_2$), $\partial(p)=\partial(p_1)=\partial(p_2)=(\partial(p)^{+}, \partial(p)^{-})$.

Let $R_{all}$ be the set of all parallel pairs of paths in a given diagram.
The diagram commutes iff
$\forall (p,q)\in R_{all}$,
$f(p)=f(q)$; that is, the composition of maps along any path connecting any pair $u$ to $v$ is independent of path choice.

\paragraph{Problems.}
